\textbf{Political Instability and Financial Markets}

### 2017-08-23 doc/paper.tex
Updated Table 1 to explicitly use Polity IV definitions of regime type

\section{Data}
Political data are primarily drawn from the Center for Systemic Peace's (CSP) Polity IV Coup d'etat dataset and Coup d'etat Events handbook. The Coup d'etat dataset includes the date of 1) successful coups, 2) attempted coups, 3) plotted coups and 4) alleged coup plots. We focus on successful coups because it is difficult to classify failed coups.\footnote{\citep[p. 617]{needler1966political} has even gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting.''} As even successful coups can have disparate outcomes (e.g. a shift from authoritarian rule to democratic rule, or vica versa), we provide a list of coups and their general outcome in \autoref{tab:coup list} below.

\singlespacing
\footnotesize
\begin{center}
\begin{longtable}[!ht]{l@{\extracolsep{\fill}}lll}
\caption{List of Coup d'Etat}
\label{tab:coup list}\\
\vspace{-5pt}\\
\hline
\multicolumn{1}{c}{Coup Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Coup Outcome}\\\hline
\endfirsthead
\multicolumn{3}{c}%
{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
\hline
\hline
\multicolumn{1}{c}{Coup Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Coup Outcome}\\\hline
\hline
\endhead
\hline 
\multicolumn{3}{r}{\textit{Continued on next page}} \\
\endfoot
\hline
\endlastfoot
06/08/1970 & Argentina & Authoritarian to authoritarian\\
03/22/1971 & Argentina & Authoritarian to authoritarian\\
03/24/1976 & Argentina & Democratic to authoritarian\\
10/06/1976 & Thailand & Democratic to authoritarian\\
10/20/1977 & Thailand & Authoritarian to authoritarian\\
12/12/1979 & South Korea & Authoritarian to authoritarian\\
02/23/1991 & Thailand & Democratic to authoritarian\\
04/05/1992 & Peru & Democratic to authoritarian\\
10/12/1999 & Pakistan & Democratic to authoritarian\\
10/04/2002 & Nepal & Democratic to authoritarian\\
09/19/2006 & Thailand & Democratic to authoritarian\\
01/11/2007 & Bangladesh & Authoritarian to authoritarian\\
04/11/2002 & Venezuela & Partial/failed authoritarian to democratic\\
\hline
\hline
\end{longtable}
\end{center}
\doublespacing
\normalsize

>>>>

\section{Data}
Political data are primarily drawn from the Center for Systemic Peace's (CSP) Polity IV Coup d'etat dataset and Coup d'etat Events handbook. The Coup d'etat dataset includes the date of 1) successful coups, 2) attempted coups, 3) plotted coups and 4) alleged coup plots. We focus on successful coups because it is difficult to classify failed coups.\footnote{\citep[p. 617]{needler1966political} has even gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting.''} As even successful coups can have disparate outcomes (e.g. a shift from authoritarian rule to democratic rule, or vica versa), we provide a list of coups and their general outcome as defined by the Polity IV Project in \autoref{tab:coup list} below.

\singlespacing
\footnotesize
\begin{center}
\begin{longtable}[!ht]{l@{\extracolsep{\fill}}lll}
\caption{List of Coup d'Etat}
\label{tab:coup list}\\
\vspace{-5pt}\\
\hline
\multicolumn{1}{c}{Coup Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Coup Outcome}\\\hline
\endfirsthead
\multicolumn{3}{c}%
{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
\hline
\hline
\multicolumn{1}{c}{Coup Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Coup Outcome}\\\hline
\hline
\endhead
\hline 
\multicolumn{3}{r}{\textit{Continued on next page}} \\
\endfoot
\hline
\endlastfoot
06/08/1970 & Argentina & Autocracy to autocracy\\
03/22/1971 & Argentina & Autocracy to autocracy (democracy by 1973)\\
03/24/1976 & Argentina & Democracy to autocracy\\
10/06/1976 & Thailand & Anocracy to autocracy\\
10/20/1977 & Thailand & Autocracy to autocracy\\
12/12/1979 & South Korea & Autocracy to autocracy\\
02/23/1991 & Thailand & Anocracy to anocracy\\
04/05/1992 & Peru & Democracy to anocracy\\
10/12/1999 & Pakistan & Democracy to autocracy\\
10/04/2002 & Nepal & Democracy to autocracy\\
09/19/2006 & Thailand & Democracy to anocracy\\
01/11/2007 & Bangladesh & Democracy to autocracy\\
 & \begin{tabular}[x]{@{}c@{}}\\\end{tabular} & \\
04/11/2002 & Venezuela & Partial/failed anocracy to democracy\\
\hline
\hline
\end{longtable}
\end{center}
\doublespacing
\normalsize
